`r params$title`

### 2024-02-04 Assets/tmp_plots/reject_reports/n_iter_300_ntry_5000_1107.qmd
reject_abc report automation

#post_dat_l |> filter(Model == "EXAM", Fit_Method == "Test",id==1) |> arrange(rank)
# head(post_dat_l)

@@

@@

## Posterior Predictive: 
```{r, fig.width=12, fig.height=14}
#| eval: true
group_predictive_plots(post_dat_l)
group_best_plots(post_dat_l)
```

```{r fig.width=12, fig.height=14}
plot_indv_posterior(ind_fits_df |> mutate(Group=condit))

## Model Comparison:
```{r, fig.width=12, fig.height=17}
#| eval: true
indv_best_plots(post_dat_l)

post_dat_l |> group_by(condit,Model,Fit_Method,rank) |> 
   summarise(mean_error=mean(abs(error)), n=n()) |> 
   ggplot(aes(x=rank,y=mean_error,fill=Model))+geom_col()+facet_wrap(~Fit_Method)

post_dat_l |> group_by(condit,Model,Fit_Method,rank,x) |> 
   summarise(mean_error=mean(abs(error)), n=n()) |> 
   ggplot(aes(x=rank,y=mean_error,fill=Model))+geom_col()+facet_wrap(Fit_Method~x,ncol=6)

post_dat_l |> group_by(condit,Model,Fit_Method,rank,x) |> 
  #filter(id==1) |>
   summarise(mean_error=mean(abs(error)), n=n()) |> 
   ggplot(aes(x=rank,y=mean_error,fill=Model))+geom_col()+facet_wrap(~Fit_Method)
```

## Individual Predictive Plots

```{r}
indv_predictive_plots(post_dat_l, ids2)
indv_predictive_plots(post_dat_l, idsBad)
```

### Subject 1
```{r fig.width=11, fig.height=12}

indv_predictive_dist((post_dat_l |> filter(rank<=200)),ind_fits_df, sbj=list(1))
abc_tables(post_dat_l |> filter(id==1))$et_sum |> gt::gt()

#post_dat |> filter(id==1,rank==1) |> group_by(Model,Fit_Method) |> slice(1)
post_dat |> filter(id==1,rank==1) |> group_by(Model,Fit_Method,x) |> 
  mutate(e2=abs(y-pred)) |> 
  summarise(y=mean(y), pred=mean(pred), me=mean(mean_error), mean_error=mean(e2)) |>
  group_by(Model,Fit_Method) |> 
  summarise(mean_error=mean(mean_error),me=mean(me))

# plot_indv_posterior(ind_fits_df |> filter(id==1))
# ind_fits_df |> filter(id==1, Fit_Method=="Test Only", Model=="EXAM") |> pull(c) |> unique()

### Subject 36
```{r fig.width=11, fig.height=12}

indv_predictive_dist(post_dat_l,ind_fits_df, sbj=list(36))
abc_tables(post_dat_l |> filter(id==36))$et_sum |> gt::gt()

# plot_indv_posterior(ind_fits_df |> filter(id==1))
# ind_fits_df |> filter(id==1, Fit_Method=="Test Only", Model=="EXAM") |> pull(c) |> unique()
```

### Best Predictions
```{r fig.width=11, fig.height=8}
abc_tables(post_dat_l |> filter(rank<=10))$et_sum |> gt::gt()

>>>>

post_dat_l |> filter(Model == "EXAM", Fit_Method == "Test",id==1) |> arrange(rank)

# head(post_dat_l)

@@

post_tabs$et_sum |> select(condit,Fit_Method,Avg_ALM_error, Avg_EXAM_error) |> filter(Fit_Method=="Test")

abc_tables(post_dat_l |> filter(rank<=10))$et_sum |> gt::gt()

@@
